A Heuristic Approach towards Drawings of Graphs with High Crossing Resolution

### 2018-05-16 paper/paper.tex
Description of the crossing computation (to be finished with Lukas) and of the gridding.

\subsection{Grid drawings: an interesting variant.}
\label{ssec:grid}

>>>>

\subsection{Grid drawings: An interesting variant.}
\label{ssec:grid}

The algorithm, as it has been described so far, does not necessarily produce grid drawings, i.e., drawings in which the vertices are at integer coordinates. However, it can be easily adjusted to produced such drawings. Recall that, at the $i$-th iteration step, our algorithm chooses uniformly at random a vertex $v_i$ from the vertex-pool and determines a set of $\rho$ feasible points $\pi_1,\ldots,\pi_\rho$. If we round these points to their closest grid points, say $\overline{\pi}_1,\ldots,\overline{\pi}_\rho$, and use them as candidates for the next position of $v_i$, then the obtained drawing will be grid, assuming that the starting drawing is grid (the latter requirement is not difficult to be achieved, e.g., by slightly adjusting the positions of the vertices of a circular layout, whose underlying circle has large radius, so to be at grid points).

An alternative approach is to let our algorithm compute a (non-grid) drawing and then apply some technique to convert it to grid. Critical here is not to affect the crossing resolution too much during the conversion. To this end, we can use a technique that is also based on randomization. For each vertex in the computed drawing, we can chose uniformly at random one of the grid points that are neighboring the vertex, and move the vertex to this point, assuming of course that there is no other vertex at this point.
